### 2022-11-08 files/Chapter2/generalvibrationmodel.tex
improvements chapter 2

  The test functions $T[0,1]$ do not form a complete space. Let $V(0,1)$ be the closure of {$F_1(0,1)$} in $H^1(0,1)$. The product space {$V(0,1)\times V(0,1)$} is denoted by $V$ and is complete. $V$ is called the energy space.\\

@@

\subsubsection{Problem T-2W}\label{sssec:existence:ProblemT2W}
Find a function $u$ such that $\forall \ t \in J$, $u(t) \in V$, $\ddot{u}(t) \in W$ and
\begin{eqnarray*}
	c(\ddot{u}(t),v) + b(u(t),v) & = & (Q(t),v)
\end{eqnarray*}
for all $v\in V$.\\

@@

As mentioned before, if $a = 0$ then the inequalities in \eqref{weak_damping} hold trivially. However, the operator A is defined by the operator $\Lambda$ and in the definition of $\Lambda$, the form $a$ is used (see \eqref{author_mapping}).\\

\vspace{10mm}
 derivation of this linear operator remains unchanged as presented in \cite{VV02} for $a$ identically zero.\\
 \vspace{10mm}

  To apply Theorem 2, the admissible initial conditions are $u_0 \in E_b$ and $u_1 \in V$. As mentioned $\langle u_0, u_1 \rangle \in D(A)$. From semigroup theory, it follows that $u(t) \in D(A)$ for each $t$. Therefore $u(t) \in E_b$ and $u'(t) \in V$ for each $t$.\\

\textcolor{red}{Volgende Rondte}\\
 Using the assumptions \textbf{A1}-\textbf{A4}, they prove that this linear operator $A$ is an infinitesimal generator of a $C_0$-semigroup of contractions and the domain of $A$ is dense in $H$.

@@

\textcolor{red}{ALLES NOG NIE BEWYS NIE - moet nog doen}

 To apply the theory, Problem T-2W must satisfy assumptions \textbf{A1}-\textbf{A4} and the initial values must be admissible.

\subsubsection{Assumption A1}\label{sssec:existence:AssumptionA1}
It is clear that $W$ is dense in $X$. (The set $W = X$).\\

Let $u \in C_0^\infty(0,1)$. Then $u(0) = u(1) = 0$ and therefore $u \in T(0,1)$ and $C_0^\infty(0,1) \subset T(0,1)$. Recall that $V(0,1)$ is the closure of $T(0,1)$ in $H^1(0,1)$.\\

So it follows that $C_0^\infty(0,1) \subset V(0,1) \subset H^1(0,1)$. And since $C_0^\infty(0,1)$ is dense in $L_2(0,1)$, both $V(0,1)$ and $H^1(0,1)$ are dense in $L_2(0,1)$. Therefore $V(0,1)\times V(0,1)$ is dense in $X = L_2(0,1) \times L_2(0,1)$.

\subsubsection{Assumption A2}\label{sssec:existence:AssumptionA2}
	From the definition of the bilinear form $c$, 
\begin{eqnarray*}
	c(f,f) & = & \int_0^1  (f_1)^2 + \frac{1}{\alpha}\int_0^1  (f_2)^2 = ||f_1||^2 + \frac{1}{\alpha}||f_2||^2.\\
\end{eqnarray*}
From this, the following inequalities can be obtained: 
\begin{eqnarray*}
	\min\left\{1, \frac{1}{\alpha}\right\} ||f||_{X}^2 \leq	c(f,f)	\leq \max\left\{1, \frac{1}{\alpha}\right\} ||f||_{X}^2.\\
\end{eqnarray*}

@@

\newtheorem*{Poincare_2}{Corollary}
\begin{Poincare_2}
	Suppose that $f \in H^1(a,b)$, and $f(0) = 0$. Then $||f|| \leq (b-a)||f'||$
\end{Poincare_2}

To show that assumption \textbf{A3} holds, it is required to show that there exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.\\

Let $f \in V$, then $f_1(0) = f_2(0) = 0$.
\begin{eqnarray}
	b(f,f) & = &   \int_0^1 (f_1'-f_2)^2 + \frac{1}{\beta}\int_0^1  (f_2')^2 \nonumber\\
	& = & ||f_1' - f_2||^2 + \frac{1}{\beta}||f_2'||^2 \nonumber\\
	& \geq & \min\left\{1 ,\ \frac{1}{\beta} \right\} \left( ||f_1' - f_2||^2 + ||f_2'||^2\right) \label{b}
\end{eqnarray}

 Using the Corollary, and from the definition of the norm $||\cdot||_X$, the following Poincar\'e-Type inequality for the norm $||\cdot||_X$ can be obtained.
\begin{eqnarray*}
	||f||_X^2 & \leq & ||f_1'||^2 + ||f_2'||^2 \\
	& = & ||f_1'||^2 -||f_2||^2 + ||f_2'||^2 +||f_2||^2\\
	& \leq & 2||f_1'-f_2||^2 + 2||f_2'||^2.
\end{eqnarray*} \sout{by Proposition 2 and the reverse triangle inequality.}\\

Using \eqref{b} and the inequality above, it follows that
\begin{eqnarray}		
	b(f,f)	& \geq & \frac{1}{2}\min\left \{1, \frac{1}{\beta}\right \} ||f||_{X}^2. \label{b2}
\end{eqnarray} for all $f \in V$.\\

Since $b$ is the bilinear form for $V$ and $W = X$, \eqref{b2} is equivalent to \[||v||^2_V \geq C^{\frac{1}{2}}_V ||v||^2_W\] for all $v \in V$ with $\displaystyle C^{\frac{1}{2}}_V = \frac{1}{2}\min\left \{1, \frac{1}{\beta}\right \} > 0$. It follows that $\displaystyle||v||_W \leq C_V||v||_V$ for all $v \in V$.\\

\sout{Since $b$ is a bilinear form and from the inequality above, $b$ is a inner-product for $V$. Using the inequality \eqref{C} results in $||v||^2_V \geq  C_3 ||w||_{W}^2$ for all $v \in V$, $w \in W$. With $C_3 =\frac{1}{2}\min\left \{1, \frac{1}{\beta}\right \} > 0$. The result follows by taking the square on both sides of the inequality.}\\

Consider \textbf{Assumption A4}. In Problem T-2W, it is clear that the bilinear form $a$ is identically zero. As mentioned before... \textcolor{red}{As mentioned before, if $a = 0$, the weak damping as well as assumption \textbf{A4} is satisfied.}\\

\section{Modal analysis}\label{sec:existence:ModalAnalysis}
\subsection{Timoshenko beam}
In this dissertation, the eigenvalues and eigenvectors of the models presented are required. To understand what is meant by modal analysis, it is in the first place necessary to consider modes of vibration. And to understand how modal analysis is applied, a Timoshenko beam is used as an example. Specifically, Problem T-1.\\

Consider the partial differential equations of a pinned-pinned Timoshenko beam (obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations1D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion1D}).
\begin{eqnarray*}
	\partial^{2}_{t} w &=& \partial_{x}(\partial_{x} w - \phi), \label{eq:1D_Model:ModalPDE1}\\
	\gamma \partial^{2}_{t} \phi &=& \beta (\partial_{x} w - \phi) + \partial_{x}(\partial_{x}\phi),\label{eq:1D_Model:ModalPDE2}
\end{eqnarray*}
with boundary conditions
\begin{eqnarray*}
	w(0,t) = 0, & &	\	 w(1,t) = 0. \label{eq:1D_Model:ModalBC1}\\
	M(0,t) = 0, & &	\	M(1,t) = 0, \label{eq:1D_Model:ModalBC2}
\end{eqnarray*}
The boundary conditions of the moments can be written in terms of $\phi$ using the constitutive equation \eqref{eq:1D_Model:ConstitutiveEquations1D}:
\begin{eqnarray*}
	\partial_{x}\phi(0,t) = 0, & & \partial_{x}\phi(1,t) = 0. \label{MA_4}
\end{eqnarray*}
Consider a trial solution $w(x,t) = T(t)\tilde{w}(x)$ with $\phi(x,t) = T(t)\tilde{\phi}(x)$. Simple substitution confirms that this trial solution satisfies the partial differential equations and the boundary conditions for Problem T-1.\\

@@

@@

\textcolor{red}{Res moet dalk out of skuif.*******************************}\\
It is now possible to test the trial solutions $w(x,t) = T(t)\tilde{w}(x)$ and $\phi(x,t) = T(t)\tilde{\phi}(x)$. Consider the right hand side of the variational form of Problem T-1V with $Q=0$. Then substituting the pair of trial solutions:
\begin{eqnarray*}
	-\int_{0}^{1}\partial_x w v'  + \int_{0}^{1} \phi v' &=& -T\int_{0}^{1} \tilde{w}' v'  + T\int_{0}^{1} \tilde{\phi} v',\\
	- \int_{0}^{1} \alpha \partial_x w \psi + \int_{0}^{1} \alpha \phi \psi - \frac{1}{\gamma} \int_{0}^{1}\partial_x \phi \psi' &=& - T\int_{0}^{1} \alpha \tilde{w}' \psi + T\int_{0}^{1} \alpha \tilde{\phi} \psi - \frac{1}{\gamma} T\int_{0}^{1} \tilde{\phi}' \psi'.
\end{eqnarray*}
Similarly for the left hand side and using \eqref{eq:1D_Model:ModalAnalysisT}:
\begin{eqnarray*}
	\int_{0}^{1} \partial_{t}^{2} w v &= \int_0^1 \ddot{T} \tilde{w} v &= T\int_0^1 \lambda \tilde{w} v,\\
	\int_{0}^{1} \partial_{t}^{2} \phi \psi &= \int_0^1 \ddot{T} \tilde{\phi} \psi &= T \int_0^1 \lambda \tilde{\phi} \psi.
\end{eqnarray*}

This shows that the pair of trial solutions $\langle {w} \ {\phi} \rangle$ are solutions of the variational problem Problem T-1V with $\langle \tilde{w} \ \tilde{\phi} \rangle$ the eigenvalues with corresponding eigenvalue $\lambda$ from the variational eigenvalue problem Problem T-1EV. This was accomplished without using the method of separation of variables and thus avoiding any contention on division by zero.\\

@@

Consider Problem XX in Section 2.2 \textbf{*** Sy reference is \eqref{GV_PB1}}\\

Given $g \in C((a,b);W)$, find $u$ such that for each $t > 0$, $u(t) \in V$, $u \in C^2((a,b);W)$ and
\begin{eqnarray*}
	c(u''(t),v) + b(u(t),v) = c(g(t),v).
\end{eqnarray*}

Now suppose there exists $\lambda$ and $x \in V$, $x \neq 0$ such that
\begin{eqnarray*}
	b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
\end{eqnarray*}

>>>>

The test functions $T[0,1]$ do not form a complete space. Let $V(0,1)$ be the closure of {$F_1(0,1)$} in $H^1(0,1)$. The product space {$V(0,1)\times V(0,1)$} is denoted by $V$ and is complete. It is called the energy space.\\

@@

\subsubsection{Problem T-2W}\label{sssec:existence:ProblemT2W}
Find a function $u$ such that $\forall \ t \in J$, $u(t) \in V$, $\ddot{u}(t) \in W$ and
\begin{eqnarray*}
	c(\ddot{u}(t),v) + b(u(t),v) & = & (Q(t),v)
\end{eqnarray*}
for all $v\in V$. The initial conditions $u(0) = u_0$ and $\dot{u}(0)=u_1$ must be specified.\\

@@

As mentioned before, if $a = 0$ then the inequality in \eqref{weak_damping} hold trivially. However, the operator A is defined by the operator $\Lambda$ and in the definition of $\Lambda$, the form $a$ is used (see \eqref{author_mapping}). It is proved in \cite{VV02} that equation \eqref{author_mapping} is uniquely solvable and hence $\Lambda$ is well defined. The proof remains unchanged as presented for $a$ identically zero.\\

To apply Theorem 2, the admissible initial conditions are $u_0 \in E_b$ and $u_1 \in V$. As mentioned above, this implies $\langle u_0, u_1 \rangle \in D(A)$. From semigroup theory, it follows that $U(t) \in D(A)$ for each $t$. Therefore $u(t) \in E_b$ and $u'(t) \in V$ for each $t$.\\

Using the assumptions \textbf{A1}-\textbf{A4}, it is proved in \cite{VV02} that the linear operator $A$ is an infinitesimal generator of a $C_0$-semigroup of contractions and the domain of $A$ is dense in $H$ (see Section \ref{sec:existence:ModalAnalysis}).

@@

To apply the theory, Problem T-2W must satisfy assumptions \textbf{A1}-\textbf{A4} and the initial values must be admissible. We must show that the assumptions are satisfied.\\

To prove \textbf{Assumption A1}, observe that $W$ is dense in $X$. (The set $W = X$).\\

Let $u \in C_0^\infty(0,1)$. Then $u(0) = u(1) = 0$ and therefore $u \in T(0,1)$ and $C_0^\infty(0,1) \subset T(0,1)$. Recall that $V(0,1)$ is the closure of $T(0,1)$ in $H^1(0,1)$. So it follows that $C_0^\infty(0,1) \subset V(0,1) \subset H^1(0,1)$. And since $C_0^\infty(0,1)$ is dense in $L_2(0,1)$, both $V(0,1)$ and $H^1(0,1)$ are dense in $L_2(0,1)$. Therefore $V(0,1)\times V(0,1)$ is dense in $X = L_2(0,1) \times L_2(0,1)$.\\

Consider \textbf{Assumption A2}. From the definition of the bilinear form $c$,
\begin{eqnarray*}
	c(f,f) & = & \int_0^1  (f_1)^2 + \frac{1}{\alpha}\int_0^1  (f_2)^2 = ||f_1||^2 + \frac{1}{\alpha}||f_2||^2.\\
\end{eqnarray*}
From this, the following inequalities can be obtained:
\begin{eqnarray*}
	\min\left\{1, \frac{1}{\alpha}\right\} ||f||_{X}^2 \leq	c(f,f)	\leq \max\left\{1, \frac{1}{\alpha}\right\} ||f||_{X}^2.\\
\end{eqnarray*}

@@

\newtheorem*{Poincare_2}{Corollary}
\begin{Poincare_2}
	Suppose that $f \in H^1(a,b)$, and $f(0) = 0$. Then $||f|| \leq (b-a)||f'||$.
\end{Poincare_2}
\begin{proof}
a
\end{proof}

There exists a positive constant $C_{V}$ such that $\Vert v\Vert_{W} \leq C_{V}\Vert v\Vert_{V}$ for each $v \in V$.
\begin{proof}
	Let $f \in V$, then $f_1(0) = f_2(0) = 0$. Using the Corollary, and from the definition of the norm $||\cdot||_X$, the following inequality for the norm $||\cdot||_X$ can be obtained.
	\begin{eqnarray*}
		||f||_X^2 & \leq & ||f_1'||^2 + ||f_2'||^2 \\
		& = & ||f_1'||^2 -||f_2||^2 + ||f_2'||^2 +||f_2||^2\\
		& \leq & 2||f_1'-f_2||^2 + 2||f_2'||^2.
	\end{eqnarray*}

	It follow from the inequality \eqref{C} that
	\begin{eqnarray}
		\Vert f \Vert_{W}^2 \leq 2C_2||f_1'-f_2||^2 + 2C_2||f_2'||^2. \label{f}
	\end{eqnarray}

	\begin{eqnarray}
		b(f,f) & = &   \int_0^1 (f_1'-f_2)^2 + \frac{1}{\beta}\int_0^1  (f_2')^2 \nonumber\\
		& = & ||f_1' - f_2||^2 + \frac{1}{\beta}||f_2'||^2 \nonumber\\
		& \geq & \min\left\{1 ,\ \frac{1}{\beta} \right\} \left( ||f_1' - f_2||^2 + ||f_2'||^2\right) \label{b}
	\end{eqnarray}

	Now combine the inequalities \eqref{f} and \eqref{b},
	\begin{eqnarray*}
		||f||_W^2 \leq Kb(f,f)
	\end{eqnarray*} for all $f \in V$.
\end{proof}

Consider \textbf{Assumption A4}. In Problem T-2W, it is clear that the bilinear form $a$ is identically zero. As mentioned before, if $a = 0$, the weak damping as well as assumption \textbf{A4} is satisfied. Also, as explained in Section \ref{sec:existence:ExistenceAndUniqueness} the constuction of the operator $A$ is not affected.\\

\section{Modal analysis}\label{sec:existence:ModalAnalysis}
\subsection{Timoshenko beam}
 To understand what is meant by modal analysis, it is in the first place necessary to consider modes of vibration. And to understand how modal analysis is applied, a Timoshenko beam is used as an example. Specifically, Problem T-1. \textcolor{red}{******* WHY NOT T-2???}\\

Consider the partial differential equations of a pinned-pinned Timoshenko beam (obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations1D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion1D}).
\begin{eqnarray*}
	\partial^{2}_{t} w &=& \partial_{x}(\partial_{x} w - \phi), \label{eq:1D_Model:ModalPDE1}\\
	\gamma \partial^{2}_{t} \phi &=& \beta (\partial_{x} w - \phi) + \partial_{x}(\partial_{x}\phi),\label{eq:1D_Model:ModalPDE2}
\end{eqnarray*}
with boundary conditions
\begin{eqnarray*}
	w(0,t) = 0, & &	\	 w(1,t) = 0. \label{eq:1D_Model:ModalBC1}\\
	M(0,t) = 0, & &	\	M(1,t) = 0, \label{eq:1D_Model:ModalBC2}
\end{eqnarray*}
The boundary conditions of the moments can be written in terms of $\phi$ using the constitutive equation \eqref{eq:1D_Model:ConstitutiveEquations1D}:
\begin{eqnarray*}
	\partial_{x}\phi(0,t) = 0, & & \partial_{x}\phi(1,t) = 0. \label{MA_4}
\end{eqnarray*}
Consider a trial solution $w(x,t) = T(t)\tilde{w}(x)$ with $\phi(x,t) = T(t)\tilde{\phi}(x)$. \\

@@

Simple substitution confirms that the trial solution satisfies the partial differential equations and the boundary conditions for Problem T-1.\\

@@

@@

Consider Problem GVar in Section 2.2.\\

Suppose there exists a number $\lambda$ and $x \in V$, $x \neq 0$ such that
\begin{eqnarray*}
	b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
\end{eqnarray*}
